Timely Object Recognition

### 2012-11-10 writeups/nips12/evaluation.tex
done with camera ready

Then there are instantiations of our method, as described in the previous section : \textbf{RL w/ Direct} inference and \textbf{RL w/ MRF} inference.
In experiments, the two were not exceedingly different in performance, with the \textbf{MRF} model consistently outperforming \textbf{Direct}.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.9\linewidth]{../figures/trajectories.pdf}
  \caption{
Visualizing the action trajectories of different policies.
Action selection traces are plotted in orange over many episodes; the size of the blue circles correspond to the $\Delta ap$ obtained by the action.
We see that the \textbf{Random} policy selects actions and obtains rewards randomly, while the \textbf{Oracle} policy obtains all rewards in the first few actions.
The \textbf{Fixed Order} policy selects actions in a static optimal order.
Our policy does not stick a static order but selects actions dynamically to maximize the rewards obtained early on.
}
  \label{fig:trajectories}
\end{figure}

\begin{table}[t]
\caption{The areas under the AP vs. Time curve for different experimental conditions.}
\label{tab:results}
\begin{center}
\begin{tabular}{|l|l|l|l|l|l|}
\hline
Bounds & Random & Fixed Order & RL w/ MRF & w/ GIST         & Oracle \\ \hline
(0,20) & 0.250  & 0.342       & 0.378     & \textbf{0.382}  & 0.488 \\ 
(0,10) & 0.119  & 0.240       & 0.266     & \textbf{0.267}  & 0.464 \\ 
(5,15) & 0.257  & 0.362       & 0.418     & \textbf{0.420}  & 0.530 \\ \hline
\end{tabular}
\end{center}
\end{table}

>>>>

Then there are instantiations of our method, as described in the previous section : \textbf{RL w/ Direct} inference and \textbf{RL w/ MRF} inference.
As the \textbf{MRF} model consistently outperformed \textbf{Direct} by a small margin, we report results for that model only.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.9\linewidth]{../figures/trajectories.pdf}
  \caption{
Visualizing the action trajectories of different policies.
Action selection traces are plotted in orange over many episodes; the size of the blue circles correspond to the increase in AP obtained by the action.
We see that the \textbf{Random} policy selects actions and obtains rewards randomly, while the \textbf{Oracle} policy obtains all rewards in the first few actions.
The \textbf{Fixed Order} policy selects actions in a static optimal order.
Our policy does not stick a static order but selects actions dynamically to maximize the rewards obtained early on.
}
  \label{fig:trajectories}
\end{figure}

\begin{table}[t]
\caption{The areas under the AP vs. Time curve for different experimental conditions.}
\label{tab:results}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Bounds & Random & Fixed Order & RL        & RL w/ GIST         & Oracle \\ \hline
(0,20) & 0.250  & 0.342       & 0.378     & \textbf{0.382}  & 0.488 \\ 
(0,10) & 0.119  & 0.240       & 0.266     & \textbf{0.267}  & 0.464 \\ 
(5,15) & 0.257  & 0.362       & 0.418     & \textbf{0.420}  & 0.530 \\ \hline
\end{tabular}
\end{center}
\end{table}

### 2012-11-10 writeups/nips12/nips2012.tex
done with camera ready

\author{
Sergey Karayev \\
UC Berkeley
\And
Tobias Baumgartner \\
Affiliation
\And
Mario Fritz \\
MPI Saarbr\"{u}cken
\And
Trevor Darrell \\
UC Berkeley
}

@@

\begin{abstract}
In a large visual multi-class detection framework, the timeliness of results can be crucial.
Our method for \emph{timely} multi-class detection aims to give the best possible performance at any single point after a start time; it is terminated at a deadline time.
Toward this goal, we formulate a dynamic, \emph{closed-loop} policy that infers the contents of the image in order to decide which detector to deploy next.
In contrast to previous work, our method significantly diverges from the predominant greedy strategies, and is able to learn to take actions with deferred values.
We evaluate our method with a novel \emph{timeliness} measure, computed as the area under an Average Precision vs. Time curve.
Experiments are conducted on the eminent PASCAL VOC object detection dataset.
If execution is stopped when only half the detectors have been run, our method obtains $66\%$ better AP than a random ordering, and $14\%$ better performance than an intelligent baseline.
On the timeliness measure, our method obtains at least $11\%$ better performance.
Our method is easily extensible, as it treats detectors and classifiers as black boxes and learns from execution traces using reinforcement learning.
\end{abstract}

@@

As always with reinforcement learning problems, defining the reward function requires some manual work.
Here, we derive it for the novel detection AP vs. Time evaluation that we suggest is useful for evaluating efficiency in recognition.
Although computation devoted to scheduling actions is less significant than the computation due to running the actions, an interesting future research direction is to explicitly consider this decision-making cost; the same goes for feature computation costs.
The code for our method is available\footnote{\url{http://sergeykarayev.com/work/timely/}}.

>>>>

\author{
Sergey Karayev \\
UC Berkeley
\And
Tobias Baumgartner \\
RWTH Aachen University
\And
Mario Fritz \\
MPI for Informatics 
\And
Trevor Darrell \\
UC Berkeley
}

@@

\begin{abstract}
In a large visual multi-class detection framework, the timeliness of results can be crucial.
Our method for \emph{timely} multi-class detection aims to give the best possible performance at any single point after a start time; it is terminated at a deadline time.
Toward this goal, we formulate a dynamic, closed-loop policy that infers the contents of the image in order to decide which detector to deploy next.
In contrast to previous work, our method significantly diverges from the predominant greedy strategies, and is able to learn to take actions with deferred values.
We evaluate our method with a novel \emph{timeliness} measure, computed as the area under an Average Precision vs. Time curve.
Experiments are conducted on the PASCAL VOC object detection dataset.
If execution is stopped when only half the detectors have been run, our method obtains $66\%$ better AP than a random ordering, and $14\%$ better performance than an intelligent baseline.
On the timeliness measure, our method obtains at least $11\%$ better performance.
Our method is easily extensible, as it treats detectors and classifiers as black boxes and learns from execution traces using reinforcement learning.
\end{abstract}

@@

As always with reinforcement learning problems, defining the reward function requires some manual work.
Here, we derive it for the novel detection AP vs. Time evaluation that we suggest is useful for evaluating efficiency in recognition.
Although computation devoted to scheduling actions is less significant than the computation due to running the actions, the next research direction is to explicitly consider this decision-making cost; the same goes for feature computation costs.
Additionally, it is interesting to consider actions defined not just by object category but also by spatial region.
The code for our method is available\footnote{\url{http://sergeykarayev.com/work/timely/}}.
